%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Augustin Peyrard's CV
%
% from
% K-CV -- Klenske Curriculum Vitae
%
% Simplified Friggeri CV
% by Edgar Klenske (ed.klenske@gmx.de)
% https://github.com/eklenske/CV
%
% Forked from:
% Jelmer Tiente
% https://github.com/JelmerT/CV
%
% Based on original work by:
% Adrien Friggeri (adrien@friggeri.net)
% https://github.com/afriggeri/CV
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{k-cv} % Add 'print' as an option into the square
                       % bracket to remove colors from this template
                       % for printing


\begin{document}
\header{Augustin}{Peyrard}{Software Engineer} % Your name and current job

%-------------------------------------------------------------------------------
%	SIDEBAR SECTION
%-------------------------------------------------------------------------------

\begin{aside} % In the aside, each new line forces a line break
\section{contact}
11 Brewster st.
San Francisco, CA 94110
~
(415) 996-8306
~
\href{mailto:augustin.peyrard@gmail.com}{augustin.peyrard@gmail.com}
\end{aside}

%-------------------------------------------------------------------------------
%	ABOUT ME SECTION
%----------------------------------------------------------------------------------------

\section{about me}
\begin{freetext}
{I am passionate about crafting software and frameworks.
I especially enjoy learning new skills and sharing my experience through challenging projects.
I worked for medium and large size software companies and startups.
I have over 19 years of experience in software engineering.}
\end{freetext}

%-------------------------------------------------------------------------------
%	EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
\section{experience}

\begin{entrylist}
%------------------------------------------------
\entry
{2020 \to now}
{Betterworks (Performance management solutions)}
{San Francisco, CA}
{\emph{Principal Engineer} \\
- Designed and implemented the event driven architecture. Abstraction layer using Apache Kafka to share and replicate data asynchronously between our Microservices.\\
- Designed with other tech leaders our new micro service architecture in order to break our legacy monolith architecture.\\
- Designed and implemented pipelines to transform and load data into our Warehouse in real time.\\
- Managed integration between Hyphen and Betterworks platforms.\\
- Designed new scalable solution to perform advanced analytics.\\
\emph{
Technologies involved:
Kafka, Golang, Debezium, Python, Postgres, Kinesis, Spark
}}
%------------------------------------------------
\entry
{2017 \to 2020}
{Hyphen (Engagement software)}
{San Francisco, CA}
{\emph{Lead Developer} \\
Worked on design and implementation of Hyphen backend architecture, built custom REST router, designed and implemented test framework.\\
Designed and implemented asynchronous jobs architecture.\\
Designed a new React application.\\
Technical lead of a team based in Bangalore.\\
\emph{
Technologies involved:
Typescript, Python, Mongodb, React, Redux-Saga, Heroku
\\ Hyphen has been acquired by Betterworks in early 2020.
}}
%------------------------------------------------
\entry
{2013 \to 2017}
{A-SIS (Supply chain software solutions)}
{Saint-Etienne, France}
{\emph{Lead Developer} \\
Worked in a team of four to create a framework written in Java/Javascript,
 the base for all company products.
The main goal was to ease new feature development process and integration as well as software reliability,
  using fine granularity components architecture (hot reloadable/deployable components with isolated responsibility). \\
\emph{
Technologies involved:
Java, Javascript, Angularjs, Hibernate, Junit, Mockito, Docker, 
Maven, REST, Websockets, Jetty, Rabbitmq
}}
%------------------------------------------------
\entry
{2015}
{A-SIS}
{Saint-Etienne, France}
{\emph{Lead Developer} \\
Worked on a prototype for ``smart'' picking shelves, presented during supply-chain exhibition in Paris.
Micro-service based architecture, shipped in a raspberry pi to control leds and range finders
(used for localization and gestures). \\
\emph{
Technologies involved:
Java, Javascript, Angularjs, Websockets, Gradle, Jetty, Raspberry Pi
}}
\end{entrylist}

\clearpage

\smallheader{Augustin}{Peyrard}

\begin{entrylist}
%------------------------------------------------
\entry
{2008 \to 2013}
{A-SIS}
{Saint-Etienne, France}
{\emph{Software engineer} \\
 I was a developer in a Research and Development team.
The team was working on the company’s main products and various technical tasks.
\begin{itemize}
\item
Lead developer for a ``rendez-vous'' warehouse planner (1 year). \\
\emph{Java, Javascript, JEE, Jboss, Oracle, Ant, Ivy}
\item
Developer of a new WMS application of the company, written in JEE (2 years). \\
\emph{Java, JEE, Jboss, Oracle, Ant, Ivy}
\item
Involved in other products for technical challenges (rule engine, conveyor algorithm, performance improvement) \\
\emph{Java}
\end{itemize}}
%------------------------------------------------
\entry
{2007 \to 2008}
{Imagina International (ERP solutions)}
{Grenoble, France}
{\emph{Software Engineer} \\
Developer in a team of three, working on development of
new features for ERP solutions and on redesigning the billing engine. \\
\emph{
Technologies involved:
Java, Tomcat, SQLServer
}}
%------------------------------------------------
\entry
{2005 \to 2007}
{CapGemini (consulting)}
{Grenoble, France}
{\emph{Software Engineer}
\begin{itemize}
\item
Developer in a project for Schneider Electric.
The goal of the project was to create a software to manage paper and electronic product
catalogues of the company.
Backend integration with a SAP/R3 and a documentum environment. \\
\emph{Java, Javascript, Struts, SOAP Webservices, WebSphere, RAD, Clearcase}
\item
During 6 months, involved in several projects, for minor improvements, maintenance or production shipping.
\end{itemize}}
%------------------------------------------------
\entry
{2003 \to 2004}
{France Telecom R\&D (telecom)}
{Grenoble, France}
{\emph{Intern} \\
Participated in the development of CLIF,
a load injection application (hosted by ObjectWeb consortium).
I developed the execution engine for load injection scenario in Java,
and created a scenario language with an IDE like management software (based on Eclipse). \\
\emph{Java, SWT/JFace}}
%------------------------------------------------
\end{entrylist}

% \clearpage

% \smallheader{Augustin}{Peyrard}

% \begin{entrylist}


%-------------------------------------------------------------------------------
%	SIDE PROJECT SECTION
%-------------------------------------------------------------------------------

\section{side projects}

\begin{entrylist}
%------------------------------------------------
\entry
{2014 \to now}
{Committer on restx (http://restx.io)}
{}
{A lightweight REST framework.
Essentially involved and interested by the dependency injection engine (brought generics management to the DI engine).
\emph{Java, Java annotation processors}}
%------------------------------------------------
\end{entrylist}

\clearpage

\smallheader{Augustin}{Peyrard}

%-------------------------------------------------------------------------------
%	TECHNOLOGY SUMMARY SECTION
%-------------------------------------------------------------------------------

\section{technologies}

\begin{freetext}
{
\textbf{Languages:} Golang, Python, Java, Typescript, C, SQL, Bash, Perl\\
\textbf{Played with:} Rust, Clojure, Ocaml, Prolog, C++, C\#, Swift, Kotlin, Scala\\
\textbf{Systems:} Linux, Unix, MacOS\\
\textbf{Frameworks:} React, AngularJS 1.x, JEE, Struts, CORBA, Junit, Mockito\\
\textbf{Tools:} GIT, SVN, Maven, Ant, Ivy, Jenkins, Jira, IntelliJ IDEA, command line (GNU utils, zsh, vim, tmux), Docker, Vagrant\\
\textbf{Streaming/Processing Platforms:} Kafka, Spark\\
\textbf{Message Brokers:} RabbitMQ\\
\textbf{Application Servers:} JbossAS, Tomcat, Jetty, Websphere\\
\textbf{Database:} Oracle, Postgresql, MySql, MongoDB\\
\textbf{Methodology:} Code review, TDD, Agile scrum\\
}
\end{freetext}

%-------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------
\section{education}

\begin{entrylist}
%------------------------------------------------
\entry
{2004}
{Master's degree {\normalfont in Software engineering}}
{Universit\'{e} Joseph Fourier, Grenoble, France}
{Specialization in networks and distributed systems}
%------------------------------------------------
\end{entrylist}


%-------------------------------------------------------------------------------
%	HOBBIES SECTION
%-------------------------------------------------------------------------------

\section{hobbies}
\vspace{-0.2cm}
\begin{freetext}
{
\begin{itemize}
  \item
  Sport: Handball, table tennis, running.
  \item
  Cooking
  \item
  Devoxx, some JUGs and vJUGs.
  Developer's Meet-ups.
\end{itemize}
}
\end{freetext}

\end{document}
